\section{Fractal Self-Traversal Along the Light Axis}
\paragraph*{Definition 3.1 (Light axis of a stratum). The light axis of stratum Sn is}
Ln := {qn $\in$Sn : |qn|2 = 0} = {qn : (ct)2 = |z1|2 + |z2|2 + |z3|2}, the set of null-norm biquaternions on Sn. In sector coordinates: Ln = {z : $\tau$n(z) = 0} = {z : tn = |z-|}.
\paragraph*{Theorem 3.2 (Fractal structure of the Sphaera). The Sphaera-Cascade $\hat K$ :}
Sn $\to$Sn-1 maps light axes to light axes: $\hat K$(Ln) = Ln-1. The global light axis is L := \ n$\geq$0 Ln = S0 = {z-= 0}, the photon sector. The Sphaera is a fractal structure whose self-traversal follows the light axis of every stratum Lorentz transformation.
\paragraph*{Proof. On Ln: $\tau$n = 0, i.e. tn = |z-|. The cascade projection $\Pi$n : Sn $\to$Sn-1}
is the Heisenberg compensator C composed with the stratum projection: it maps z-7$\to$1 2(z-+J(z-)) = 0 for any z-on the light axis (since J(z-) = -zon Ln). Hence $\hat K$(Ln) $\subseteq${z-= 0} = S0 = Ln-1. Inductively, L = S0.
\paragraph*{Remark (Triolic Z/3Z structure on the light axis). On each Ln, the three kernels}
z1, z2, z3 are phase-shifted by 120: z1 = |z| $\cdot$ ei$\cdot$0, z2 = |z| $\cdot$ ei$\cdot$2$\pi$/3, z3 = |z| $\cdot$ ei$\cdot$4$\pi$/3, satisfying z1 + z2 + z3 = 0 (the compensation condition). This Z/3Z phase symmetry is an additional structure on Ln; it is compatible with the SU(3) rotation symmetry of the triple (z1, z2, z3). The cascade $\hat K$ preserves this triolic structure at every level.

