\section*{Historical Open Questions (status-synchronized)}
\addcontentsline{toc}{section}{Historical Open Questions (status-synchronized)}
The list below is retained for proof-memory and cross-reference continuity.
It should not be read as a list of equally open fronts. Some entries are now
only \emph{residual quantitative tasks}, while others are already closed as
separate historical OPs. In particular, nothing in the list below should be
read as license to reopen the visible interface fixed in the 3.5 record stage:
the remaining work is downstream of the residual record in the present stabilized reading, not parallel to it.

\begin{enumerate}
  \item \textbf{Structural completion: observer frame from first principles}
        \textbf{[reduced residual open].}
        The value $\beta_{\mathrm{sym}} \approx 0.5493$ is determined from
        $\gamma_{\mathrm{BI}}$ and $\gamma_{\mathrm{string}}$. Its remaining
        open content is no longer the broad existence of a frame candidate,
        but the explicit derivation of the prime-lattice / continuum-limit
        correction that moves the continuum fixed-point candidate to the
        measured matter-frame value.

  \item \textbf{Field equation / controlled emergence [open].}
        A natural variational candidate is
  \[
  \delta \int R \, \tau_n^2 \, d\mu = 0.
  \]
        What remains open is the fully controlled derivation of Einstein- and
        Dirac-type projections with explicit constants, error bounds, and
        approximation control.

  \item \textbf{Spectrum: mass hierarchy [open].}
        The heuristic relation $m_p \sim \sqrt{p}\,m_P$ has the correct
        qualitative structure, but the map from prime/spectral index to
        Standard-Model quantum numbers is still unknown.

  \item \textbf{Spectrum: three generations [open].}
        The chain $S_2 \supset S_1 \supset S_0$ is structurally compatible
        with three fermion generations, but no quantitative derivation is
        given here.

  \item \textbf{Structural completion: Dixon algebra [open].}
        A compact reformulation in $\mathbb{C} \otimes \mathbb{H} \otimes
        \mathbb{O}$ (dimension $64$) may unify the present results in a
        single algebraic object.

  \item \textbf{Historical OP~2: Dirac operator on $\Hplusminus$ [closed as a separate OP].}
        The existence, essential self-adjointness, and GOE-class parts are
        already closed in the present text. The former T4 frame-offset part is
        no longer separate and is absorbed into Item~1 above.

  \item \textbf{Historical OP~3: Koide / $\theta_K$ formula [closed at the present structural level].}
        The Koide/triolic block should remain available for later proof-density
        enrichment, but it should no longer be counted among the primary open
        problems of the present version.

  \item \textbf{Historical OP~5: photon-frame $\Lambda$-cancellation [reduced residual open].}
        Step~(A) of the photon-frame $\Theta$--$R$ program is already closed.
        The remaining live content is Step~(B), i.e.\ the exact
        $\Theta$-sum / $\Theta$--$R$ balance at the photon-frame cutoff.
\end{enumerate}

\clearpage
