\section*{v2.11.0 Multi-Readout Consistency and Fusion Core}
\addcontentsline{toc}{section}{v2.11.0 Multi-Readout Consistency and Fusion Core}

\begin{quote}
\textbf{Normalization note (v2.17.1 local review).}
This block is retained as a \emph{historical multi-readout and fusion precursor}. It remains relevant as supporting proof memory, but no longer functions as an independent primary structural core in the normalized architecture.
\end{quote}

The reconstruction layer from v2.10.0 promotes readable modes into theorem-level
observables. The next structural question is what happens when several
reconstructions are all individually admissible but are intended to describe one
and the same structural content. The task of v\docversion\ is therefore not merely
to extract observables, but to fuse them without creating contradictory readouts,
without hiding overlap behind notation, and without allowing probe-local views to
break the ambient closure architecture. This introduces a multi-readout
consistency layer.

\subsection*{1. Readout families and consistency targets}
Let $\{\mathcal R_j\}_{j\in J}$ be a family of admissible reconstruction maps,
possibly associated with different filter systems, theorem contexts, or probe
resolutions. For a given state $u$ one obtains a readout family
\[
\mathrm{Obs}_j(u)=\mathcal R_j\bigl((\mathcal F^{(j)}_\alpha u)_\alpha\bigr).
\]
The purpose of the new layer is to decide when the collection
$\{\mathrm{Obs}_j(u)\}_{j\in J}$ should be regarded as several compatible views of one
structural object rather than several unrelated observables. Compatibility is
measured against the same closure, budget, and tagging rules that already govern
the single-readout setting.

\paragraph{Principle 5 (multi-readout consistency).}
A family of theorem-level observables may be fused only when their mutual
discrepancies are either controlled by a visible ledger term or assigned to
explicit source tags. Silent disagreement is not an allowed mode of structural
multiplicity.

\subsection*{2. Consistency ledger and fusion defect}
Introduce a fusion-defect functional
\[
\mathfrak D_{\mathrm{fus}}(u)
:= \sum_{j<k}\nu_{jk}\,\|\mathrm{Obs}_j(u)-\Gamma_{jk}\mathrm{Obs}_k(u)\|_{\mathfrak O_*},
\]
where $\Gamma_{jk}$ transports the $k$-th observable into the comparison frame of the
$j$-th observable and the coefficients $\nu_{jk}\ge 0$ encode structural relevance.
The associated consistency ledger is then
\[
\mathrm{CL}(u):=\mathfrak D_{\mathrm{fus}}(u)+\mathrm{Tag}(u)+\mathrm{Leak}(u).
\]
A family is called fusion-admissible when $\mathrm{CL}(u)$ stays below the threshold
prescribed by the theorem context. Thus disagreement is not denied; it is made
visible, budgeted, and therefore manageable.

\subsection*{3. Fused observable and anti-inflation rule}
Whenever the family is fusion-admissible, define a fused observable
\[
\mathrm{Obs}_{\mathrm{fus}}(u)=\sum_{j\in J}\lambda_j\,\Gamma_j\mathrm{Obs}_j(u)-\Xi(u),
\]
where the coefficients $\lambda_j$ are admissible weights, $\Gamma_j$ transports to a
common observable frame, and $\Xi(u)$ is an anti-inflation compensator correcting
for visible overlap and recorded fusion defect. The fused observable is required
to satisfy an estimate of the form
\[
\|\mathrm{Obs}_{\mathrm{fus}}(u)\|_{\mathfrak O_*}
\le C_{\mathrm{fus}}
\bigl(
\sum_{j\in J}\|\mathrm{Obs}_j(u)\|_{\mathfrak O_j}
-\mathrm{OL}_{\mathrm{fus}}(u)
+\mathrm{CL}(u)
\bigr),
\]
so that fusion cannot enlarge theorem-level content by counting the same readable
structure several times through nominally different channels.

\subsection*{4. HC-stable fusion and theorem transport}
The fused observable must still respect HC confinement. One therefore asks for
\[
\Pi_{\mathrm{HC}}\,\mathrm{Obs}_{\mathrm{fus}}(u)
=\mathrm{Obs}_{\mathrm{fus}}(u)+\rho(u),
\qquad
\|\rho(u)\|_{\mathfrak O_*}
\le C_{\rho}\,\mathrm{CL}(u).
\]
This means that multi-readout fusion is accepted only if the residual mismatch is
fully visible in the same ledger that already recorded comparison defects. In
addition, theorem transport must preserve fusion status: if a fused observable is
moved into a lemma, table, or appendix tool, the same fusion certificate must
remain available after transfer.

\subsection*{5. Probe/ambient coherence under fusion}
In the two-probe sector one may have ambient and probe reconstructions of the same
structural feature. The new requirement is that the probe fusion defect be bounded
by ambient fusion defect plus descent mismatch:
\[
\mathfrak D^{\mathrm{probe}}_{\mathrm{fus}}(v)
\le C_{\mathrm{coh}}
\bigl(
\mathfrak D_{\mathrm{fus}}(u)+\mathrm{Mismatch}(u,v)
\bigr).
\]
Hence probe readouts do not become a second autonomous truth layer; they inherit
coherence from the ambient structure, up to visible descent error.

\subsection*{6. Consequence for appendix tools}
The appendix tool taxonomy is refined again. A strong appendix item may now be
labelled as a fusion certificate, consistency-ledger estimate, anti-inflation
compensator, theorem-transport witness, or probe-coherence bound. This fits the
user's structural preference that tools be collected as reusable proof interfaces
rather than scattered informally through the running text.

\subsection*{7. v\docversion\ readiness criterion}
The present step should be regarded as successful if the following can now be
done:
\begin{itemize}
  \item several admissible reconstructions can be compared in one explicit ledger;
  \item disagreements between readouts are tagged or budgeted instead of hidden;
  \item fused observables remain protected against overlap inflation;
  \item probe and ambient readouts satisfy a visible coherence estimate; and
  \item appendix transfer preserves not only observables, but also their fusion certificates.
\end{itemize}

This is the gain of v\docversion. The companion monolith now carries not only
closure, channel specialization, transport dynamics, forward invariance,
field-energy realization, semigroup readout, spectral admissibility, filtered
observability, and trace reconstruction, but also a first disciplined fusion
layer for theorem-level observables. Future field equations are therefore
constrained five times: they must generate the correct ledger-dissipative
semigroup, belong to the correct resolvent class, pass a trace-compatible readout
filter, admit HC-stable observable reconstruction, and finally support
multi-readout fusion without hidden inconsistency.


% ------------------------------------------------------------------
% Appendix: Structural Tools and Regime Tests (v2.27.4 integration)
% ------------------------------------------------------------------

