\section*{Bibliographic hardening scan for v\docversion}
\addcontentsline{toc}{section}{Bibliographic hardening scan for v\docversion}

\noindent The r06 scan was conservative: it did not alter the theorem chain and did not promote any external source to an axiom. It only checked which external literatures are repeatedly invoked by terminology, analogies, or mathematical background in the monolith and then expanded the terminal bibliography accordingly. The highest-priority additions are Teichmuller/quasiconformal references, because Teichmuller, Beltrami, and quasiconformal language occurs often while the r05 bibliography had no dedicated Teichmuller anchor. The second-priority additions are the Riemann--GUE/RMT and operator/spectral references, because the document repeatedly uses GUE pacing, Riemann-zero language, and self-adjoint/spectral framing. The third-priority additions are structural background references for Hopf/fibre bundles, division algebras, gauge/QFT landmarks, CKM/PMNS mixing, Julia dynamics, ZF/set theory, and the probe/cryptographic/computational diagnostic vocabulary.

\noindent The present bibliography is therefore still not meant to be exhaustive. In particular, a later release could still add a dedicated literature group for Teichmuller geodesic flow, measured foliations, moduli-space dynamics, geometric quantization, modern $G_2$ model building, neutrino phenomenology, and numerical zeta-zero datasets. Those are useful follow-on enrichments, but they are not required for the r06 hardening pass.

\clearpage
