
\maketitle
\thispagestyle{fancy}

\begin{center}
\fbox{\begin{minipage}{0.92\textwidth}
\small
\textbf{Companion status.} The governing prior public baseline is the \emph{v3.34.0 public split-bundle release}. The present text is the \emph{v3.35.0 pre-v4 QAM reindexing, two-sided tensor-notation, and mixed-readout release}. The concept DOI remains the title-page pointer. The version-specific Zenodo DOI for this public release is recorded in the Version and DOI record below, not as a mathematical object name. This release prepares, but does not perform, the future v4 QAM Hilbert-shift that reserves tag 0 for the empty/no-active-kind marker, and it adds a conservative two-sided structural tensor notation as a local compression grammar for readout/action/comparison roles.

\medskip
\noindent\textbf{Theorematic status.} OP~1/4 and OP~5(B) remain open. The new store, snapshot, clone, rollback, scrub, mirror, stripe, and parity/residual language is infrastructure and audit vocabulary only; it does not manufacture closure certificates.
\end{minipage}}
\end{center}
\vspace{0.6em}


\begin{abstract}
Version~\docversion{} is a pre-v4 readability and QAM-infrastructure preparation release built on the public v3.34.0 split-bundle release. It keeps the Active Core / Historical Witness separation, retains the QAM/MML/MMA store-array infrastructure, and introduces a conservative plan for the later QAM Hilbert-shift: the current inhabited tuple tags are not migrated in this version, but a future v4 line may shift each inhabited QAM tag one step upward so that tag 0 can be reserved for the empty or no-active-kind marker. The present version also defines mixed QAM readouts only as guarded derived packages over already admissible component readouts, together with an optional binary mask registry for IPv4-like Boolean filtering of readout kinds. New in r02 is a conservative two-sided structural tensor notation that marks readout-facing, structure-facing, comparison, and selector roles without changing classical tensor contraction. The r03 layer stabilizes that notation by adding role-erasure, guarded mixed-readout normal forms, Boolean mask grammar, and explicit proof-neutrality. The r04 layer is the release-candidate freeze/audit pass that packages those additions and records that no global QAM Hilbert-shift, no primitive mixed-tensor activation, and no OP closure is being claimed. The present release-final layer inserts the assigned public version DOI in the release records and leaves theorematic content unchanged. These additions are routing, audit, and preparation tools. They do not close OP~1/4 or OP~5(B), do not assert Turing-completeness, do not activate primitive mixed tensors, and do not turn the Sphaera array parity/residual layer into a technical RAID reconstruction theorem.
\end{abstract}

\clearpage
