\section{Fractal Self-Traversal Along the Light Axis}
\label{sec:fractal}
%% ============================================================

\begin{remark}[Structural null axis and physical light-axis readout]
In the structurally prior language of the Companion, the distinguished
axis selected by the MM/HC architecture is the null axis. Once the same
axis is read at stable physical propagation level, it appears as the
light axis. Thus the present section keeps the historically familiar
light-axis title, while treating it explicitly as the physical readout
of a structurally prior null-axis statement.
\end{remark}

\begin{definition}[Light axis of a stratum]
The structurally prior null axis of stratum $S_n$ is
\[
L_n:=\{q_n\in S_n:|q_n|^2=0\}.
\]
At the physical propagation readout of the same architecture, this null
axis is read as the light axis of $S_n$.
\end{definition}

\begin{theorem}[Fractal structure of the Sphaera]\label{thm:fractal}
The Sphaera-Cascade
\[
\KC:S_n\to S_{n-1}
\]
transports the null axis of each stratum to the null axis of the next:
\[
\KC(L_n)=L_{n-1}.
\]
The global null axis is therefore
\[
L=\bigcap_{n\ge 0}L_n=S_0,
\]
where $S_0$ is the terminal compensated photon sector.
Hence the self-traversal of the Sphaera is fractal in the precise sense
that the same null-axis structure is carried through all strata by the
same MM/HC architecture and appears physically as the light axis at
stable readout.
\end{theorem}

\begin{proof}
By the general MM-tools, the cascade does not generate a new object at
each stratum, but transports one and the same structural content through
admissible realization levels.

By the HC-tools, the null sector is precisely the sector whose
frame-sensitive imbalance is removed by the compensator while its
structural identity is preserved.
Thus the cascade does not replace the null axis; it carries the same
null-axis structure from one stratum to the next.

Therefore
\[
\KC(L_n)=L_{n-1}.
\]
Iterating this transport through the whole cascade yields the terminal
compensated null sector
\[
L=\bigcap_{n\ge 0}L_n=S_0,
\]
which is read physically as the photon/light sector.
\end{proof}

\begin{remark}[Triolic $\mathbb{Z}/3\mathbb{Z}$ structure on the null/light axis]
On the transported null axis, read physically as the light axis at stable propagation, the three kernels remain organized by the
triolic phase condition
\[
z_1+z_2+z_3=0.
\]
Thus the cascade preserves the structural $\mathbb{Z}/3\mathbb{Z}$
pattern while driving the frame-sensitive component to the compensated
photon/light sector.
\end{remark}

%% ============================================================

