\section{Gauge Structure of the Standard Model}
\begin{quote}\small
\noindent\textbf{Status.} \emph{Legacy physical-readout block inside the active main body.}\par
\noindent\textbf{Block function.} This section explains how the structural core is read as a gauge-sector organization rather than as an independently added physical layer.
\end{quote}
\label{sec:gauge}
%% ============================================================

\begin{proposition}[$\HH\otimes\mathbb{C}\to U(1)\times SU(2)$]
\label{prop:biquaternion-u1su2}
The biquaternion algebra $\HH\otimes_{\mathbb{R}}\mathbb{C}$ generates
exactly the gauge group $U(1)\times SU(2)$.
\end{proposition}

\begin{proof}
\emph{$SU(2)$ from unit quaternions.}
The unit quaternions $\{q\in\HH:|q|=1\}\cong S^3$ form a Lie group
isomorphic to $SU(2)$.
The three generators are $T_k:=\sigma_k/2$ (half Pauli matrices),
satisfying $[T_j,T_k]=i\varepsilon_{jkl}T_l$.

\emph{$U(1)$ from the complex scalar.}
The imaginary time unit $it\in i\mathbb{R}$ generates the abelian group
$e^{i\theta}\in U(1)$ for $\theta\in\mathbb{R}$.
This commutes with all $SU(2)$ generators.
Hence $U(1)\times SU(2)$, direct product.
\end{proof}

\begin{theorem}[$\OO\to SU(3)$]\label{thm:octonion-SU3}
The octonions decompose under $SU(3)$-action as
$\OO = \mathbb{C}\oplus\mathbb{C}^3$,
a singlet plus the fundamental (triplet) representation of $SU(3)$.
The triplet $\mathbb{C}^3$ carries the three kernels $(K_1,K_2,K_3)$
as the three colors.
\end{theorem}

\begin{theorem}[Standard Model from the Sphaera biquaternion]\label{thm:SM}
The biquaternion ground state $q_n\in\HH\otimes\mathbb{C}$, extended to
the octonionic structure $\mathbb{C}\otimes\HH\otimes\OO$, generates
the Standard Model gauge group $U(1)\times SU(2)\times SU(3)$ with
generators arising from:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lll}
\toprule
Source & Group & Physical force\\
\midrule
Complex scalar $it$ & $U(1)$ & Electromagnetism\\
Unit quaternions $\HH$ & $SU(2)$ & Weak force\\
Octonion triplet $\mathbb{C}^3\subset\OO$ & $SU(3)$ & Strong force\\
\bottomrule
\end{tabular}
\end{center}
\end{theorem}

\begin{proof}
Propositions 7.1--7.2 and Theorem~\ref{thm:octonion-SU3} establish each
factor.
The three factors are independent (direct product structure) because
$U(1)$ commutes with $SU(2)$ and both commute with the $SU(3)$ action
on $\mathbb{C}^3$: the $SU(3)$ generators $\lambda_k$ act only on the
color indices, not on the quaternion structure.
\end{proof}

%% ============================================================

