\section{From HC Decomposition to a QFT Lagrangian}
\begin{quote}\small
\noindent\textbf{Status.} \emph{Legacy physical-readout block inside the active main body.}\par
\noindent\textbf{Block function.} This section translates the compensator decomposition into a Lagrangian-style readout without reopening the underlying structural core.
\end{quote}
\label{sec:lagrangian}
%% ============================================================

\begin{remark}[The Lagrangian is already implicit]
The HC decomposition $\Hplus=\Hplusplus\oplus\Hplusminus$ of \S\ref{sec:stringlqg}
carries a complete QFT operator structure.
This section makes it explicit as a three-term Lagrangian density.
\end{remark}

\begin{definition}[Sphaera QFT Lagrangian]\label{def:lagrangian}
For $f\in\Hplus$ with frame offset $\bsym$, define:
\begin{align}
  \mathcal{L}_{\mathrm{kin}}(f)
    &:= \langle f,\,L_0 f\rangle,\label{eq:L_kin}\\
  \mathcal{L}_{\mathrm{HC}}(f)
    &:= \langle C(f),\,L_0\,C(f)\rangle,\label{eq:L_HC}\\
  \mathcal{L}_{\mathrm{frame}}(f)
    &:= \bsym^2\,\langle f,f\rangle.\label{eq:L_frame}
\end{align}
The full Lagrangian density is
\[
  \mathcal{L}(f)
  \;=\;
  \mathcal{L}_{\mathrm{kin}}(f)
  \;-\;
  \mathcal{L}_{\mathrm{HC}}(f)
  \;-\;
  \mathcal{L}_{\mathrm{frame}}(f).
\]
\end{definition}

\begin{theorem}[$J$-gauge invariance of $\mathcal{L}$]\label{thm:gauge-invariance}
$\mathcal{L}(f)$ is invariant under the $J$-gauge transformation
$f\mapsto Jf$:
\[
  \mathcal{L}(Jf) = \mathcal{L}(f).
\]
\end{theorem}

\begin{proof}
$\mathcal{L}_{\mathrm{kin}}$:
$\langle Jf,L_0 Jf\rangle = \langle f,J^{-1}L_0 Jf\rangle
= \langle f,L_0 f\rangle$
by $\mathrm{Adj}_J(L_0)=0$ (\cite{brendecke2026rh}, Theorem~9.2).

$\mathcal{L}_{\mathrm{HC}}$:
$C(Jf)=\tfrac{1}{2}(Jf+J^2 f)=\tfrac{1}{2}(Jf+f)=C(f)$,
so $\mathcal{L}_{\mathrm{HC}}(Jf)=\mathcal{L}_{\mathrm{HC}}(f)$.

$\mathcal{L}_{\mathrm{frame}}$:
$\langle Jf,Jf\rangle=\langle f,J^*Jf\rangle=\langle f,f\rangle$
since $J$ is anti-unitary with $J^*J=\mathrm{id}$.
\end{proof}

\begin{theorem}[Equations of motion recover the field equation]
\label{thm:eom}
The Euler--Lagrange equation $\delta\mathcal{L}/\delta\bar f=0$ gives
\[
  \bigl(P_-+(L_0-\lambda)P_+\bigr)\Psi=0,
\]
which is the Sphaera field equation (\cite{brendecke2026rh}, Definition~8.2).
Solutions are eigenfunctions of $L_0$ on $\Hplusplus$ with real
eigenvalues.
\end{theorem}

\begin{proposition}[Frame term gives the cosmological constant]
\label{prop:lambda-from-frame}
The term $\mathcal{L}_{\mathrm{frame}}=\bsym^2\langle f,f\rangle$
contributes $\bsym^2 g_{\mu\nu}$ to the field equation via metric
variation.
In the photon frame ($\bsym=0$): $\mathcal{L}_{\mathrm{frame}}=0$
and the cosmological constant vanishes exactly.
A matter observer always measures $\Lambda_{\mathrm{obs}}\sim\bsym^2$
--- not vacuum energy, but the permanent frame offset.
\end{proposition}

\begin{remark}[The three-term structure is frame-complete]
The Lagrangian $\mathcal{L}=\mathcal{L}_{\mathrm{kin}}
-\mathcal{L}_{\mathrm{HC}}-\mathcal{L}_{\mathrm{frame}}$ encodes all
three physical layers in one object:
$\mathcal{L}_{\mathrm{kin}}$ carries the dynamics of $L_0$;
$\mathcal{L}_{\mathrm{HC}}$ enforces confinement to the admissible
sector $\Hplusplus$;
$\mathcal{L}_{\mathrm{frame}}$ records the permanent matter-frame
displacement from $\zminus=0$.
No further $\gL$-insertions are needed: all frame dependencies are
derived from this single term.
The $J$-gauge group acts as $U(1)\times SU(2)\times SU(3)$
(Theorem~\ref{thm:SM}), so $\mathcal{L}$ is automatically
Standard-Model invariant.
\end{remark}

%% ============================================================

