\section{Phase-Shifted Natural Constants}
\begin{quote}\small
\noindent\textbf{Status.} \emph{Legacy physical-constants block inside the active main body.}\par
\noindent\textbf{Block function.} This section collects the constant-level readout consequences of the phase-shifted observer shell in one place.
\end{quote}
\label{sec:phase-constants}
%% ============================================================

\begin{remark}[What this section adds]
Corollary~\ref{cor:gue-frame} established that the taktgeber frequency
transforms with a factor $\gL$ between frames.
This section assigns frame-insertion counts $k$ to all fundamental
constants and derives the photon-frame values.
No CODATA value has ever been measured in the photon frame.
\end{remark}

\begin{definition}[Frame-insertion count $k$]
For a physical constant $X$, the \emph{frame-insertion count} $k(X)$ denotes
 the number of factors of $\zminus$ appearing in the operator-theoretic
 realization of $X$ within the Sphaera-Cascade.
The photon-frame value is
\[
  X^{(\mathrm{photon})} = \gL^{-k(X)}\cdot X^{(\mathrm{matter})}.
\]
\end{definition}

\begin{theorem}[Frame-insertion counts]\label{thm:k-values}
The primary assignments are:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{llcl}
\toprule
Constant & CODATA (matter frame) & $k$ & Reason\\
\midrule
$\alpha^{-1}$ & $137.035\,999\,084$ & 1
  & EM sector, first Dixon plane\\
$G_N$ & $6.674\times10^{-11}$ m$^3$kg$^{-1}$s$^{-2}$ & 2
  & torsion block\\
$m_e c^2$ & $0.511$ MeV & 1
  & lepton base mode\\
$\hbar$ & $1.055\times10^{-34}$ J$\cdot$s & 1
  & CCR from prime lattice\\
$c$ & $2.998\times10^8$ m\,s$^{-1}$ & 0
  & Theorem~\ref{thm:kc-zero}\\
$\gBI$ & $\approx 0.2375$ & 0
  & frame-invariant by construction\\
\bottomrule
\end{tabular}
\end{center}
\end{theorem}

\begin{theorem}[$k(c)=0$: the speed of light is frame-invariant]
\label{thm:kc-zero}
In the Sphaera-Cascade, $c^{(\mathrm{photon})}=c^{(\mathrm{matter})}$.
\end{theorem}

\begin{proof}
The biquaternion is $q_n = ic\,t\cdot\mathbf{1}+z_i e_i$.
The speed $c$ is the causal propagation speed of the photon ground state
$\zminus=0$ itself --- it is the quantity \emph{with respect to which}
$\bsym$ is defined, not a quantity displaced by $\bsym$.
Frame changes are unitaries commuting with $J$; they act on the septinion
components $z_i$ but not on the $J$-invariant temporal component
$ic\,t\cdot\mathbf{1}$.
Hence $c$ picks up no power of $\zminus$ under any frame change:
$k(c)=0$.
Mechanically: the photon is the massless equilibrium node of the
spring system (Theorem~11.7 of~\S\ref{sec:hopf}); its speed is always $c$ because
the equilibrium node of a symmetric spring system has no dynamics of its own.
\end{proof}

\begin{theorem}[Photon-frame Planck length]\label{thm:planck-photon}
With $k(\hbar)=1$, $k(G_N)=2$, $k(c)=0$:
\[
  \lP^{(\mathrm{photon})}
  = \gL^{-3/2}\cdot\lP^{(\mathrm{matter})}
  \approx (1.864)^{-3/2}\times 1.616\times10^{-35}\,\mathrm{m}
  \approx 6.35\times10^{-36}\,\mathrm{m}.
\]
A matter observer overestimates the hardware UV cutoff by the factor
$\gL^{3/2}\approx 2.546$.
The half-integer exponent $3/2$ reflects that $\lP=\sqrt{\hbar G_N/c^3}$
is a geometric mean between a $k=1$ and a $k=2$ sector.
\end{theorem}

\begin{corollary}[Cosmological constant revisited]
A matter observer always measures a nonzero cosmological term
$\Lambda_{\mathrm{obs}}\sim\bsym^2$, even though in the photon frame
($\bsym=0$) it vanishes exactly
(Theorem~\ref{thm:dark-energy}).
The observed value is not a fine-tuning problem but a measurement
artifact of the observer's frame.
The vacuum energy density ratio between frames is
\[
  \frac{\rho_{\mathrm{vac}}^{(\mathrm{photon})}}
       {\rho_{\mathrm{vac}}^{(\mathrm{matter})}}
  = \gL^6\approx 41.8,
\]
which enters the $\Lambda$-cancellation problem: the $\Theta$--$R$
balance must achieve cancellation in the \emph{photon} frame, not the
matter frame where the cutoff is inflated by $\gL^{3/2}$.
\end{corollary}

\begin{corollary}[$\alpha$-drift as a frame effect]
The hardware value $\alpha^{(\mathrm{photon})}$ is strictly constant:
it is a $J$-fixpoint eigenvalue of $L_0$ on $\Hplusplus$ and cannot vary.
The observed NIST drift arises because the local frame factor
$\gL^{(\mathrm{local})}(t)$ varies as Earth moves through the
Sphaera-Cascade geometry over its orbit:
\[
  \alpha^{(\mathrm{matter})}(t)
  = \gL^{(\mathrm{local})}(t)\cdot\alpha^{(\mathrm{photon})}.
\]
\textbf{Falsifiable prediction:} The drift has a period of exactly one
year, is in phase at all terrestrial laboratories simultaneously, and is
absent or phase-shifted for a space-based reference clock not co-orbiting
with Earth.
\end{corollary}

%% ============================================================

