\section{Field Equations of the Probe--Closure System}
\begin{quote}\small
\noindent\textbf{Status.} \emph{Legacy field-equation block inside the active main body.}\par
\noindent\textbf{Block function.} This section formulates the field-equation package attached to the probe/closure interface and fixes what the later closure section has to stabilize.
\end{quote}
\label{sec:field-eq}
%% ============================================================

\begin{remark}[From probe equation to field system]
The Dirac probe equation of \S\ref{sec:dirac-probe} is the minimal
first-order transport law for a closure-preserving fermionic mode.
To pass from a single probe reading to a dynamical theory, one must
promote the closure data, the compensator, and the resonance transport
into coupled fields.
\end{remark}

\begin{definition}[Probe--closure field content]
We consider the following effective fields on spacetime:
\begin{align*}
  \Psi(x) &\in \mathcal H_{\mathrm{sept}}
    &&\text{(septonic probe spinor)},\\
  \mathcal A_\mu(x)
    &&&\text{(resonance connection)},\\
  \hat P_{C_7}(x)
    &&&\text{(Meta-Septum closure projector)},\\
  \mathcal H_C(x)
    &&&\text{(Heisenberg compensator field)}.
\end{align*}
The stable sector is defined by the projector constraint
\[
  \hat P_{C_7}^2 = \hat P_{C_7},
  \qquad
  (\mathbf 1-\hat P_{C_7})\Psi = 0.
\]
\end{definition}

\begin{definition}[Covariant probe derivative]
The effective covariant derivative of the probe--closure system is
\[
  \mathcal D_\mu
  :=
  \partial_\mu
  + i\mathcal A_\mu
  + \kappa\,\mathcal H_C\,n_\mu
  + \eta\,(\mathbf 1-\hat P_{C_7})\,n_\mu,
\]
where $n_\mu$ is the distinguished null-axis direction, read physically as the light-axis direction at stable propagation, and
$\kappa,\eta\in\mathbb R$ are effective couplings.
The last two terms encode, respectively, compensator stabilization and
penalization of departures from admissible closure.
\end{definition}

\begin{theorem}[Master probe field equation]
\label{thm:master-field-equation}
The minimal closure-compatible field equation extending
Theorem~\ref{thm:dirac-probe} is
\[
  \left(
    i\Gamma^\mu\mathcal D_\mu
    - \Omega
  \right)\Psi = 0,
\]
with effective resonance operator
\[
  \Omega
  :=
  m_0\mathbf 1
  + \alpha\,\hat P_{C_7}\mathcal M_{16}\hat P_{C_7}
  + \beta\,g_Y\,\mathcal T
  + \gamma\,\mathcal H_C.
\]
Here $m_0$ is a bare inertial scale, $g_Y$ the Yokamono coupling,
$\mathcal T$ the triadic coupling operator, and
$\alpha,\beta,\gamma\in\mathbb R$ are effective coefficients.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:dirac-probe} already fixes the first-order spinorial
character of the transport law.
The Meta-Septum constraint requires the dynamics to be projected through
$\hat P_{C_7}$, while the closure mismatch is stabilized by the
compensator field $\mathcal H_C$.
The Millennium matrix $\mathcal M_{16}$ contributes the internal
septonic resonance structure, and the Yokamono sector contributes the
triadic coupling term $g_Y\mathcal T$.
Hence the displayed equation is the minimal local first-order extension
compatible with all previously introduced structures.
\end{proof}

\begin{definition}[Curvature and closure current]
The curvature of the resonance connection is
\[
  \mathcal F_{\mu\nu} := [\mathcal D_\mu,\mathcal D_\nu].
\]
Its source decomposes into a probe current, a closure current, and a
compensator current:
\begin{align*}
  J^{(\Psi)}_\nu &:= \bar\Psi\Gamma_\nu\Psi,\\
  J^{(C_7)}_\nu &:= \lambda_C\,\partial_\nu
    \mathrm{Tr}(\mathcal M_{16}\hat P_{C_7}),\\
  J^{(HC)}_\nu &:= \lambda_H\,\partial_\nu
    \mathrm{Tr}(\mathcal H_C\mathcal M_{16}).
\end{align*}
\end{definition}

\begin{theorem}[Resonance field equation]
\label{thm:resonance-field-eq}
The effective connection field satisfies
\[
  \mathcal D^\mu\mathcal F_{\mu\nu}
  =
  J^{(\Psi)}_\nu + J^{(C_7)}_\nu + J^{(HC)}_\nu.
\]
Thus the compensator and the closure are not external constraints only,
but true dynamical source terms of the resonance transport.
\end{theorem}

\begin{quote}\small
\noindent\textbf{Reader cue.} Read the next block as a closure-tightening continuation of the same field package. Its purpose is to add the explicit closure equation, the triadic two-probe coupling, and the variational form that later closure arguments stabilize.
\end{quote}

\begin{proposition}[Closure equation]
\label{prop:closure-equation}
The Meta-Septum closure becomes a local field constraint of the form
\[
  \mathrm{Tr}(\mathcal M_{16}\hat P_{C_7})
  \equiv 0 \pmod{\mathrm{HC}},
\]
and, in dynamical form,
\[
  \mathcal H_C = \Lambda[\mathcal M_{16},\hat P_{C_7}],
\]
for an effective closure functional $\Lambda$.
Hence physically stable probe states are precisely those lying in the
$C_7$-sector.
\end{proposition}

\begin{proposition}[Triadic two-probe system]
\label{prop:triadic-two-probe}
Let $\Psi_1,\Psi_2$ be two coupled probe modes and let $\Psi_\perp$ be a
third orthogonal triadic component.
Then the combined field
\[
  \Psi_{\triangle}
  :=
  \begin{pmatrix}
    \Psi_1\\
    \Psi_2\\
    \Psi_\perp
  \end{pmatrix}
\]
satisfies a block equation
\[
  \bigl(i\Gamma^\mu\mathcal D_\mu - \Omega_{\triangle}\bigr)
  \Psi_{\triangle}=0,
\]
with
\[
  \Omega_{\triangle}
  =
  \begin{pmatrix}
    \Omega_1 & g_Y\mathcal T_{12} & 0\\
    g_Y\mathcal T_{21} & \Omega_2 & 0\\
    0 & 0 & \Omega_\perp
  \end{pmatrix}
  +
  \chi
  \begin{pmatrix}
    0 & 0 & \mathcal T_{1\perp}\\
    0 & 0 & \mathcal T_{2\perp}\\
    \mathcal T_{\perp1} & \mathcal T_{\perp2} & 0
  \end{pmatrix}.
\]
Therefore the triadic component is not decorative but enters as an
intrinsic coupling channel of the effective field system.
\end{proposition}

\begin{theorem}[Variational form]
\label{thm:variational-form}
The probe--closure system is generated by the effective action
\[
  S
  =
  \int d^4x\,
  \Bigl(
    \bar\Psi i\Gamma^\mu\mathcal D_\mu\Psi
    - \bar\Psi\Omega\Psi
    - \tfrac14\mathrm{Tr}(\mathcal F_{\mu\nu}\mathcal F^{\mu\nu})
    - U_{C_7}
    - U_{HC}
  \Bigr),
\]
where
\[
  U_{C_7}
  :=
  \lambda_C\,
  \bigl\|(\mathbf 1-\hat P_{C_7})\Psi\bigr\|^2,
  \qquad
  U_{HC}
  :=
  \lambda_H\,
  \bigl\|\mathcal H_C - \Lambda[\mathcal M_{16},\hat P_{C_7}]\bigr\|^2.
\]
Its Euler--Lagrange equations are exactly the master probe equation,
the resonance field equation, and the closure equation above.
\end{theorem}

\begin{remark}[Status of the construction]
This section does not yet claim a derivation of Einstein's equations or
of the Standard Model Lagrangian.
It provides instead the first internally closed field architecture of
the Sphaera probe sector: the Dirac probe, the Meta-Septum closure, the
Millennium matrix, the Yokamono coupling, and the Heisenberg
compensator are now written as one coupled variational system.
The next task is the explicit closing of the system, namely the concrete
realization of $\Lambda[\mathcal M_{16},\hat P_{C_7}]$ and the direct
computation of the closure residue.

\end{remark}

%% ============================================================

