\section{HC-Induced Readout Geometry and Structural Unity}
\label{sec:theorem7}

\subsection*{Setup}

Let $\mathcal{K}$ be a closure-stable structural kernel, and let
\[
  \mathcal{R}_f : \mathcal{K} \to \mathcal{O}_f
\]
be admissible readout maps corresponding to different regimes (ART,
QFT, probe). Let $\mathcal{H}_C$ denote the Heisenberg compensator,
understood as a structural object controlling compatibility between
readouts. This is the concrete realization of
Definition~\ref{def:readout-relative-lemma}: each $\mathcal{R}_f$
produces a readout-relative statement, while $\mathcal{K}$ carries the
kernel-level content.

\subsection*{Theorem 7 (HC-Induced Readout Geometry)}

\begin{theorem}[HC-induced readout geometry]
\label{thm:hc-readout-geometry}
Under the above assumptions, the following statements hold.
\begin{enumerate}[label=(\arabic*)]
  \item \textbf{Readout divergence and effective trajectories.}
  For two readouts $f,g$, define
  $\Delta_{f,g} := \mathcal{R}_f - \mathcal{R}_g$.
  The induced effective dynamics in observable space generically
  produces trajectories that are not globally closed and may exhibit
  local segments resembling hyperbolic motion with apparent domain gaps.

  \item \textbf{Projection singularities.}
  Apparent gaps in trajectories correspond to incompatibilities of
  projections:
  \[
    \exists\, x \in \mathcal{K}:\quad
    \begin{aligned}
      &\mathcal{R}_f(x)\ \text{well-defined, while}\\
      &\mathcal{R}_g(x)\ \text{is not compatibly representable.}
    \end{aligned}
  \]
  These are projection singularities rather than physical
  discontinuities. In the language of
  Proposition~\ref{prop:legitimacy-restricted-lemmas}: $\mathcal{R}_f(x)$
  is a readout-relative statement whose regime of validity excludes the
  $g$-readout.

  \item \textbf{Mirror structure and recombination.}
  There exists a transformation $S$ such that locally
  $S(\mathcal{R}_f) \approx \mathcal{R}_g$.
  Complementary trajectory branches can therefore be recombined into
  an effective elliptic structure at the level of combined readouts.

  \item \textbf{Effective two-center dynamics.}
  The recombined dynamics is equivalent to motion in a symmetric
  two-center system, where the centers correspond to competing
  readout-fixed structures rather than physical sources. This is
  the bidirectional probe picture of
  Section~\ref{sec:bidirectional-probe-lensing}
  (Proposition~\ref{hyp:bidirectional-probe-lensing}) at the level of
  effective trajectories.

  \item \textbf{Non-orientable global structure.}
  The combined readout structure is generically non-orientable:
  transport along a closed loop induces a phase shift, requiring
  multiple loops for full return. This is consistent with a
  Möbius-type structure and reflects the $\zminus = \pm\bsym$
  symmetry of Theorem~\ref{thm:symmetric-frame}.

  \item \textbf{Existence of a structural lift.}
  There exists a lifted space $\tilde{\mathcal{K}}$ and projection
  $\pi : \tilde{\mathcal{K}} \to \mathcal{O}$ such that trajectories
  in $\tilde{\mathcal{K}}$ are smooth and closed, while their
  projections reproduce gaps, hyperbolic segments, and branching
  effects. This is the structural lift of
  Definition~\ref{def:structural-lift} applied to trajectory data.

  \item \textbf{HC as curvature.}
  The compensator $\mathcal{H}_C$ acts as curvature of the readout
  bundle, governing deviations of trajectories, phase shifts, and
  apparent failure of closure at the visible trajectory level. In the
  present release such failure must first be tested through native
  closure-class preservation and the OP transport theorem rather than
  inferred from raw trajectory separation alone. This is the geometric
  realization of Corollary~\ref{cor:M-HC-fixpoint}: $\mathcal{M}C = \lambda_0 C$
  fixes the compensator as the structural curvature anchor.

  \item \textbf{Projective vanishing.}
  There exist configurations such that
  \[
    \sum_i \mathcal{H}_C^{(f_i)} = 0
    \quad\text{while}\quad
    \mathcal{H}_C^{(\mathrm{kernel})} \neq 0.
  \]
  Thus the compensator may vanish in projection while remaining
  nontrivial at kernel level. This is precisely
  Remark~\ref{rem:hc-shadow-vs-core}: the shadow vanishes, not
  the kernel $C = \Pi^{(\mathcal{M})}_{\mathrm{spec}}$.

  \item \textbf{Emergent tensor structure.}
  The measurable curvature induced by $\mathcal{H}_C$ defines an
  effective tensor field $T_{\mu\nu}^{(\mathrm{HC})}$, arising from
  readout divergence $\Delta_{f,g}$ rather than from fundamental
  stress-energy. This is the tensorial compensator readout
  $\mathcal{K}_{\mu\nu}^{(\mathrm{HC})}$ of
  Hypothesis~\ref{hyp:hc-meta-generator}(iii) at the trajectory level.

  \item \textbf{Recursive field structure.}
  There exists a functional relation
  $\mathcal{F}[\mathcal{F}] = 0$,
  where $\mathcal{F}$ generates field equations recursively and
  $\mathcal{H}_C$ appears as a structural product within this
  recursion. This reflects the generating loop of
  Section~\ref{sec:hc-meta-field-generator}: the compensator is
  simultaneously generated by closure and inserted into transport.
\end{enumerate}
\end{theorem}

\begin{proof}
Statements (1)--(2) follow from the definition of $\Delta_{f,g}$ and
the readout-relative lemma framework
(Definition~\ref{def:readout-relative-lemma}): incompatible regime
projections produce apparent gaps that are projection singularities,
not structural discontinuities.

Statement (3) follows from the unitary equivalence of the three kernels
(Theorem~\ref{thm:unitary-equiv}): the transformation $S$ is the
unitary equivalence between the $f$- and $g$-readout representations.

Statement (4) is the trajectory-level reading of the bidirectional
probe picture (Section~\ref{sec:bidirectional-probe-lensing}): the two
regime probes approach the same closure-stable core from opposite sides.

Statement (5) follows from Theorem~\ref{thm:symmetric-frame}: matter
and tachyon sectors are positioned symmetrically around the photon frame
at $\pm\bsym$, so a full structural loop traverses both readout
branches.

Statement (6) is the structural lift principle
(Proposition~\ref{prop:structural-lift-principle}) applied to
trajectory data: the smooth lifted trajectories in $\tilde{\mathcal{K}}$
are the kernel-level content, while the projected gaps are readout
artifacts.

Statement (7) follows from Corollary~\ref{cor:M-HC-fixpoint}:
$\mathcal{M}C = \lambda_0 C$ identifies the compensator as the
structural fixpoint controlling all admissible transport; deviation
from this fixpoint is exactly what curvature measures.

Statement (8) is Remark~\ref{rem:hc-shadow-vs-core}: exact-sector
vanishing $\sum_i \mathcal{H}_C^{(f_i)} = 0$ is the shadow, not the
kernel $C = \Pi^{(\mathcal{M})}_{\mathrm{spec}}$
(Theorem~\ref{thm:hc-spectral-projector}).

Statement (9) follows from statement (7) and the probe-tensor readout
of Section~\ref{sec:bidirectional-probe-lensing}: the cross-bilinear
$E^a_{\mu,\mathrm{cross}}$ assembles into $T_{\mu\nu}^{(\mathrm{HC})}$.

Statement (10) is the recursive generating loop of
Hypothesis~\ref{hyp:hc-meta-generator}: the meta-field equation
$\mathfrak{E}_{\mathrm{HC}}[\ldots] = 0$ is the instance of
$\mathcal{F}[\mathcal{F}] = 0$ in the present framework.
\end{proof}

\subsection*{Interpretation}

Phenomena such as trajectory gaps, apparent singularities, or chaotic
behavior are not fundamental inconsistencies, but arise as projection
effects of a smooth, higher-dimensional structural system
(cf.\ Definition~\ref{def:kernel-level-statement}). Different physical
theories (Dirac, QFT, Einstein) correspond to distinct readouts of the
same kernel rather than incompatible foundations.

\subsection*{Methodological consequence}

Statements proven within a specific readout remain valid within that
regime. Their invariant structural content may be lifted to kernel-level
statements via structural lift, in accordance with
Section~\ref{sec:readout-relative-lemmas} and
Proposition~\ref{prop:structural-lift-principle}.

% ------------------------------------------------------------------
% Hypothesis 7.4 (v2.27.4 integration)
% ------------------------------------------------------------------

