\section{The Millennium Matrix as Global Heisenberg-Compensator}
\label{sec:millennium-hc}

\begin{definition}[Millennium matrix]
The Millennium matrix $\mathcal M_{16}$ is the global structural matrix that
transports one and the same Sphaera-object through its admissible algebraic,
closure, and projection layers. It preserves identity through viewpoint
change.
\end{definition}

\begin{definition}[Layer decomposition]
We write
\[
\mathcal M_{16}
=
\mathcal M_{\mathrm{tri}}
+
\mathcal M_{\mathrm{alg}}
+
\mathcal M_{\mathrm{cl}}
+
\mathcal M_{\mathrm{proj}},
\]
where $\mathcal M_{\mathrm{tri}}$ encodes the triolic kernel organization,
$\mathcal M_{\mathrm{alg}}$ admissible algebraic realization changes,
$\mathcal M_{\mathrm{cl}}$ closure compatibility, and
$\mathcal M_{\mathrm{proj}}$ admissible final readout.
\end{definition}

\begin{definition}[Global Heisenberg-compensator reading]
The Millennium matrix is said to be read as a global Heisenberg-compensator
matrix if its action extends the local rule
\[
C=\tfrac12(\mathrm{id}+J)
\]
to the full multi-layer architecture of the Companion. Under this reading, the
Millennium matrix is denoted by
\[
\mathcal H_{16},
\]
or identified with $\mathcal M_{16}$ when no ambiguity arises.
\end{definition}

\begin{theorem}[Structural role of the Millennium matrix]
\label{thm:mm-role}
The Millennium matrix is the global structural intermediary of the Companion in
the following sense:
\begin{enumerate}
  \item it preserves the identity of the triolic core under admissible
  realization change;
  \item it transports structural content through admissible algebraic layers
  without ontology change;
  \item it enforces closure discipline before readout;
  \item when read as $\mathcal H_{16}$, it becomes the global balancing
  mechanism for physically admissible interpretation.
\end{enumerate}
\end{theorem}

\begin{proof}
The triolic layer supplies the primitive object. The admissible algebraic
layers supply realizations of that object. Closure selects the admissible
sector, while projection only reads out what closure has stabilized. The
Millennium matrix is the unique global carrier of this ordered transport.
Under the Heisenberg-compensator reading, the same transport becomes the
global balancing mechanism across all admissible layers.
\end{proof}

