\section{Current-state instantiation}
\begin{definition}[Current frontier-certified pre-entry state]\label{def:current-frontier-preentry}
The current local state is represented by the current compact paired conservative normal form $\mathcal{N}^{\ast}_{\mathrm{curr}}$, its extracted current live residual state $\Rcurr$, its normalized state $\Rcurrtilde$, and a current admissible normalization scale triple. In the absence of an explicit current proof of close-basin or promote-region membership, the current state is read conservatively as frontier-certified pre-entry.
\end{definition}

\begin{definition}[Preferred witness class]\label{def:preferred-witness-class}
The current preferred witness class $\Wpref$ consists of strict admissible route-faithful paired witnesses that improve the horizon-side closure coordinate and provide at least one genuine packet-side improvement without destroying the current invariant class.
\end{definition}

\begin{definition}[First normalized lead witness]\label{def:first-normalized-lead-witness}
A first normalized lead witness is an element
\[
\widetilde{\mathbf{R}}_{\mathrm{lead}}\in\Wpref
\]
that minimizes the normalized weighted residual energy inside the preferred witness class and remains admissible for downstream OP-entry auditing.
\end{definition}

\begin{definition}[Lead-direction tag]\label{def:lead-direction-tag}
The current lead-direction tag records whether the dominant current gain of the lead witness is horizon-dominant, phase-dominant, envelope-dominant, or paired-mixed.
\end{definition}

\begin{definition}[Directed next witness class]\label{def:directed-next-witness-class}
If the lead witness remains frontier-classified, the directed next witness class $\Wdir$ is obtained by filtering the current witness menu according to the current lead-direction tag, so that the next successor search is directionally coherent rather than fully undirected.
\end{definition}

\begin{theorem}[Current state synthesis theorem]\label{thm:current-state-synthesis-theorem}
For the present project line, the current local state has current foundation-complete frontier status. More precisely:
\begin{enumerate}[leftmargin=2em]
  \item the pre-OP foundational package is established;
  \item the current state is conservatively read as frontier-certified pre-entry;
  \item the current state carries a current normalization scale triple and normalized residual state;
  \item the current state carries a preferred witness class, a first normalized lead witness, a lead-direction tag, and a directed next witness class.
\end{enumerate}
Consequently, the line is mathematically stabilized up to the final pre-OP transition layer.
\end{theorem}

\begin{proof}
All listed structures have already been established in the current groundwork line and then instantiated at the local level. Collecting them yields the claimed synthesis.
\end{proof}

