\begin{center}
{\LARGE\bfseries Quantum Sphaera Companion}\par\vspace{0.4em}
{\Large\bfseries Historical Witness}\par\vspace{0.8em}
{\large A preserved Part II / COMPLETE snapshot for v3.35.0}\par\vspace{0.8em}
Marc Brendecke\par
Independent Researcher, Bochum, Germany\par
Concept DOI: \href{https://doi.org/10.5281/zenodo.19210728}{10.5281/zenodo.19210728}\par
\docdate{} --- Version \docversion{} --- historical witness release
\end{center}
\thispagestyle{fancy}

\begin{quote}\small
\noindent\textbf{Status.} This PDF preserves the historical witness that was formerly integrated as Part II of the monolithic Companion. It is not deleted, shortened, or promoted into the active theorem core. It is carried as proof memory, genealogy, and reconstruction support in the same release bundle as the active core. The v3.35.0 historical witness release keeps this file separate for readability and archival clarity, not as a second theorematic line.

\medskip
\noindent\textbf{Active companion file.} The governing current proof-line is provided as\par
\texttt{Quantum\_Sphaera\_Companion\_v3\_35\_0\_active\_core\_release\_final.pdf}.

\medskip
\noindent\textbf{Reading rule.} If a historical statement sounds stronger, flatter, or older than the active-core status ledger, the active-core reading governs. In particular, this historical witness does not close OP~1/4 or OP~5(B).

\medskip
\noindent\textbf{Cross-reference rule.} References from this historical witness to labels that now live in the active core are preserved by stable label name, written as \texttt{label} in the active-core PDF, rather than imported as mutable cross-document page numbers.
\end{quote}

\clearpage
\tableofcontents
\clearpage
